### 2018-05-15 submission/manuscript.Rmd
make changes to bray-curtis --remove sub-sampling

***Minimal Bray-Curtis Differences are Detected and are Dependent on both Cycle Number and Sub-Sampling Depth:***
A few small differences based on sub-sampling and cycle number were detected in overall bacterial community composition. Within the same fecal sample and independent of HiFi DNA polymerases, there were differences in the community composition between 20 and 25 cycles that was dependent on sub-sampling depth (sub-sampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (IQR)), sub-sampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), sub-sampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Further, when data was available for the mock communities, there were larger observed differences between 20 and 25 cycles (sub-sampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. Additionally, these stated community differences disappear when comparing 25 to 30 cycles and do not persist past 25 cycles [Figure 3]. Although these trends are clearly noticeable, we found that there was no detectable difference in Bray-Curtis index when comparing to the previous 5-cycle increment for both fecal and mock communities after multiple comparison correction (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). Using PERMANOVA to test for community differences based on cycle number within HiFi DNA polymerases, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depths (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`). For fecal samples, Phusion was one of two HiFi DNA polymerases that had enough sequences to reach a sub-sampling depth of 1000 at 15 cycles. Overall, these data suggest that there are small HiFi DNA polymerase differences in Bray-Curtis index that are dependent on both sub-sampling depth and cycle number.

>>>>

***Minimal Bray-Curtis Differences are Detected and are Dependent on Cycle Number:***
A few small differences based on sub-sampling and cycle number were detected in overall bacterial community composition. Within the same fecal sample and independent of HiFi DNA polymerases, there were large differences in the community composition between 20 and 25 cycles [Figure 3A]. Additionally, when data was available for the mock communities, there were also large observed differences between 20 and 25 cycles [Figure 3B]. These community differences within a sample disappear when comparing 25 to 30 cycles and do not persist past 25 cycles [Figure 3]. Although these trends are clearly noticeable, we found that there was no detectable difference in Bray-Curtis index when comparing to the previous 5-cycle increment for both fecal and mock communities after multiple comparison correction (P-value `r ifelse(min(filter(bray_sim_to_prev_cycle_kruskal_results, sub_sample_level == 1000)[, "bh"], na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). Using PERMANOVA to test for community differences based on cycle number within HiFi DNA polymerases, only Phusion had cycle dependent differences (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`. For fecal samples, Phusion was one of two HiFi DNA polymerases that had enough sequences to be rarefied to 1000 at 15 cycles. Overall, these data suggest that there are small HiFi DNA polymerase differences in Bray-Curtis index that are dependent on cycle number.

### 2018-05-15 submission/manuscript.tex
make changes to bray-curtis --remove sub-sampling

\textbf{\emph{Minimal Bray-Curtis Differences are Detected and are
Dependent on both Cycle Number and Sub-Sampling Depth:}} A few small
differences based on sub-sampling and cycle number were detected in
overall bacterial community composition. Within the same fecal sample
and independent of HiFi DNA polymerases, there were differences in the
community composition between 20 and 25 cycles that was dependent on
sub-sampling depth (sub-sampled to 1000 = 0.51 (0.4 - 0.79) (median
(IQR)), sub-sampled to 5000 = 0.43 (0.33 - 0.63), sub-sampled to 10000 =
0.4 (0.24 - 0.43)) {[}Figure 3A{]}. Further, when data was available for
the mock communities, there were larger observed differences between 20
and 25 cycles (sub-sampled to 1000 = 0.88 (0.42 - 0.91)) {[}Figure
3B{]}. Additionally, these stated community differences disappear when
comparing 25 to 30 cycles and do not persist past 25 cycles {[}Figure
3{]}. Although these trends are clearly noticeable, we found that there
was no detectable difference in Bray-Curtis index when comparing to the
previous 5-cycle increment for both fecal and mock communities after
multiple comparison correction (P-value \textgreater{} 0.05). Using
PERMANOVA to test for community differences based on cycle number within
HiFi DNA polymerases, only Phusion had cycle dependent differences at
1000 and 5000 sub-sampling depths (P-value = 0.03 and 0.01). For fecal
samples, Phusion was one of two HiFi DNA polymerases that had enough
sequences to reach a sub-sampling depth of 1000 at 15 cycles. Overall,
these data suggest that there are small HiFi DNA polymerase differences
in Bray-Curtis index that are dependent on both sub-sampling depth and
cycle number.

>>>>

\textbf{\emph{Minimal Bray-Curtis Differences are Detected and are
Dependent on Cycle Number:}} A few small differences based on
sub-sampling and cycle number were detected in overall bacterial
community composition. Within the same fecal sample and independent of
HiFi DNA polymerases, there were large differences in the community
composition between 20 and 25 cycles {[}Figure 3A{]}. Additionally, when
data was available for the mock communities, there were also large
observed differences between 20 and 25 cycles {[}Figure 3B{]}. These
community differences within a sample disappear when comparing 25 to 30
cycles and do not persist past 25 cycles {[}Figure 3{]}. Although these
trends are clearly noticeable, we found that there was no detectable
difference in Bray-Curtis index when comparing to the previous 5-cycle
increment for both fecal and mock communities after multiple comparison
correction (P-value \textgreater{} 0.05). Using PERMANOVA to test for
community differences based on cycle number within HiFi DNA polymerases,
only Phusion had cycle dependent differences (P-value = 0.03. For fecal
samples, Phusion was one of two HiFi DNA polymerases that had enough
sequences to be rarefied to 1000 at 15 cycles. Overall, these data
suggest that there are small HiFi DNA polymerase differences in
Bray-Curtis index that are dependent on cycle number.
